### 2016-09-22 doc/publications/plos16/plos16.tex
Added table with data size scalability results
Preatiffied the table
fixed CursedForest.bib -- many duplicated entries

The digital revolution is seeing a dramatic increase in data collected about every aspect of 
life~\cite{Loebbecke2015}.  These data sets are not only growing vertically by capturing more and more events but also
horizontally by capturing more information about these events.  The challenge of big and ``wide'' data is especially
pronounced in the health space where whole genome sequence (WGS) technology enabled researchers to interrogate all 3
billion base pairs of the human genome.

@@

\begin{table}[!ht]
\centering
\caption{
{\bf Time in seconds to build random forest of 100
  trees with specified mtry fraction using given number of CPU cores.}}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
\multicolumn{2}{|l|}{\multirow{2}{*}{}}                   & \multicolumn{4}{|c|}{Number of CPU cores}  \\
                                                            &  & 16   & 32      & 64      & 128  \\
\multirow{3}{*}{mtry (fraction)}                            & 0.10 & 708.3  & 340.0  & 186.0 & 134.5 \\
                                                            & 0.25 & 1134.9 & 535.0  & 270.8 & 179.6 \\
                                                            & 0.50 & 1724.1 & 856.6  & 428.7 & 243.8 \\
                                                            & 0.80 & 2313.5 & 1125.7 & 569.1 & 364.6 \\

>>>>

The digital revolution is seeing a dramatic increase in data collected about every aspect of life~\cite{Loebbecke2015}.
These data sets are not only growing vertically, by capturing more and more events, but also horizontally by capturing
more information about these events.  The challenge of big and ``wide'' data is especially pronounced in the health
space where whole genome sequence (WGS) technology enabled researchers to interrogate all 3 billion base pairs of the
human genome.

@@

%nvars 150000  500000  2500000 10000000  50000000
%nsamples          
%1000  21.6  26.7  59.8  133.5 668.8
%5000  45.7  71.9  186.2 729.3 2887.4
%10000 70.2  120.2 397.3 2237.8  5747.8

\begin{table}[!ht]
\centering
\caption{
{\bf Time in seconds to build random forest of 100
  trees on 128 CPU cores with varying numbers of variables and samples.}}
\begin{tabular}{|l|l||l|l|l|l|l|}
\hline
\multicolumn{2}{|l||}{\multirow{2}{*}{}}               & \multicolumn{5}{c|}{Number of variables}  \\
\cline{3-7}
\multicolumn{2}{|l||}{}                                & \bf{150,000} & \bf{500,000} & \bf{2,500,000}  & \bf{10,000,000} & \bf{50,000,000} \\
\hline                                                            
\multirow{4}{*}{Number of samples}                          & \bf{1000} &  21.6 & 26.7 & 59.8 & 133.5 & 668.8 \\
                                                            & \bf{5000} & 45.7 & 71.9 & 186.2 & 729.3 & 2887.4 \\
                                                            & \bf{10000} & 70.2 & 120.2 & 397.3 & 2237.8 & 5747.8 \\
\hline
\end{tabular}
\begin{flushleft} 
\end{flushleft}
\label{table10}
\end{table}

\begin{table}[!ht]
\centering
\caption{
{\bf Time in seconds to build random forest of 100
  trees with specified mtry fraction using given number of CPU cores.}}
\begin{tabular}{|l|l||l|l|l|l|}
\hline
\multicolumn{2}{|l||}{\multirow{2}{*}{}}                   & \multicolumn{4}{|c|}{Number of CPU cores}  \\
\cline{3-6}
\multicolumn{2}{|l||}{}                                               & \bf{16} & \bf{32}      & \bf{64}      & \bf{128}  \\
\hline
\multirow{4}{*}{mtry (fraction)}                            & \bf{0.10} & 708.3  & 340.0  & 186.0 & 134.5 \\
                                                            & \bf{0.25} & 1134.9 & 535.0  & 270.8 & 179.6 \\
                                                            & \bf{0.50} & 1724.1 & 856.6  & 428.7 & 243.8 \\
                                                            & \bf{0.80} & 2313.5 & 1125.7 & 569.1 & 364.6 \\
